---
title: "ATP Tour viewed by Master SEP, prom 2023"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    css: extra.css
    vertical_layout: scroll
runtime: shiny
---


```{r include=FALSE}
#required libraries load ----
if (!require(flexdashboard)) { install.packages("flexdashboard"); library(flexdashboard) } 
if (!require(shiny)) { install.packages("shiny"); library(shiny) } 
if (!require(rlang)) { install.packages("rlang"); library(rlang) }
if (!require(shinythemes)) { install.packages("shinythemes"); library(shinythemes) } 
if (!require(tidyverse)) {install.packages("tidyverse"); library(tidyverse)}
if (!require(dplyr)) { install.packages("dplyr"); library(dplyr) }
if (!require(plotly)) { install.packages("plotly"); library(plotly) }
if (!require(ggplot2)) { install.packages("ggplot2"); library(ggplot2) } 
if (!require(ggthemes)) { install.packages("ggthemes"); library(ggthemes) } 
if (!require(DT)) { install.packages("DT"); library(DT) }
if (!require(janitor)) { install.packages("janitor"); library(janitor) } # for rownames_to_column function in Restructure_Frequent_oppo function
if (!require(readr)) { install.packages("readr"); library(readr) } # for data_importation.R to avoid multiple loads
if (!require(magrittr)) { install.packages("magrittr"); library(magrittr) } # for data_importation.R to avoid multiple loads
if (!require(forcats)) { install.packages("forcats"); library(forcats) } # for fct_reorder function in most_final_appearances function


#Required functions : out sourced extensive and simple functions
source("R/data_wrangling.R")
source("R/data_vizualisation.R")

# data importation and preparation----
source("R/data_importation.R")

```

```{css, echo=FALSE}
.fluid-row {
  font-size: 5.9vw;
}
.value-box {
  height: 110px;
}
```


```{r global, message=FALSE, warning=FALSE}
# intialise styles for value boxes ----
top_text_style <- 
"position: absolute; 
overflow: hidden; 
left: 5%; top: 1px; 
right: 0px; 
bottom: 0px; width:100%;
font-weight: 580;"

bottom_text_style <- 
"position: absolute;
bottom: 0;
left: 5px;
font-weight: 600;"

text_style <- 
"position: absolute;
bottom: 0;
left: 5px;width:100%;
font-weight: 580;"

```

# Presentation
# Overall 1968-2022 ATP tours 


# Men's Tennis records {data-orientation=rows}

## Row 1 
-------------------------------
```{r}
# To retrieve the selected Tourney value
Tourneys_list=unique(atp$tourney_name)
selectizeInput('tournoi',  'Please select a Tourney', Tourneys_list)
```
### {.value-box} 
```{r}
# Surface type valueBox
renderValueBox({
  surf_df=nb_match_surface(atp, input$tournoi)
  list=unique(surf_df$surface)
  
  value=noquote(paste(list,  collapse=", "))
  caption = tags$p("Type of Surface", style = text_style)
  valueBox(value, icon = "fas fa-ticket-alt", color="#008B8B", caption)
})
```

### {.value-box} 
```{r}
# Number of matchs played valueBox
renderValueBox({
  nb_match_df=nb_match_func(atp, input$tournoi)
    
  caption = tags$p("Number of Matches Played", style = text_style)
  valueBox(nb_match_df[1,'nb_match', drop=TRUE], icon = "fas fa-table-tennis", color="#00C5CD", caption)
})
```

### {.value-box} 
```{r}
#Longest match duration in Minutes valueBox
renderValueBox({
  duration_matchs = duration(input$tournoi, atp)
  max_duration = duration_matchs[which.max(duration_matchs$minutes),]
  
  caption = tags$p("Longest match duration in Minutes", style = text_style)
  valueBox(max_duration$minutes, icon = "fas fa-stopwatch", color="#79CDCD", caption)
})
```

### {.value-box} 
```{r}
#Shortest match duration in Minutes valueBox
renderValueBox({
  duration_matchs = duration(input$tournoi, atp)
  min_duration = duration_matchs[which.min(duration_matchs$minutes),]

  caption = tags$p("Shortest match duration in Minutes", style = text_style)
  valueBox(min_duration$minutes, icon = "fas fa-stopwatch", color="#79CDCD", caption)
})
```

### {.value-box}
```{r}
# Oldest player to win a final valueBox
renderValueBox({
  age=players_final_ages(atp, input$tournoi)
  max_age_df = age[which.max(age$winner_age),]
  
  value = tags$p(paste(max_age_df$winner_age), style = "font-size: 110%;")
  caption = div(
           tags$p("Oldest player to win a final was", style = top_text_style), 
           tags$h4(paste(max_age_df$winner_name), style = bottom_text_style))
  valueBox(value, icon = "fa fa-trophy", color="#98F5FF", caption)
})
```
### {.value-box}

```{r}
# Youngest player to win a final valueBox
renderValueBox({
  age=players_final_ages(atp, input$tournoi)
  min_age_df = age[which.min(age$winner_age),]
  
  value = tags$p(paste(min_age_df$winner_age), style = "font-size: 110%;")
  caption = div(
       tags$p("Youngest player to win a final was", style = top_text_style), 
       tags$h4(paste(min_age_df$winner_name), style = bottom_text_style))
  valueBox(value, icon = "fa fa-trophy", color="#98F5FF", caption)
})
```
## Column
------
### Players' contributions

```{r}
DT::renderDataTable({
  carriere=player_info(atp, input$tournoi)
  
  DT::datatable(carriere,fillContainer=TRUE, class = "cell-border compact") 
})
```

### Explore Top 10 players according to
```{r fig.align='center', fig.height=5.5, fig.width=8}
selectInput('explore',  '', c("Victories", "Aces"))# Retrieve the variable to explore: victories or aces
#Top 10 players based on the explore input variable
renderPlotly({
  top_10_df=Top_10(atp, input$tournoi, input$explore)
  
  fig=top_10_winners_vis(top_10_df, input$explore, "#1c8f7a", "total descending", 'Rockwell', '#009966') 
  fig <- fig %>% layout(autosize = F,width = 600, height = 420)


  fig
})
```
### Finals' ATP contributers' Ranks evolution 
```{r fig.align='center', fig.height=5.5, fig.width=8}
renderPlotly({
  table=Atp_ranks(atp, input$tournoi)
  
  fig=evolution(table)
  fig <- fig %>% layout(autosize = F,width = 660, height = 420)
  fig
})
```
## row 

### Explore Top 5 Lowest and Highest Ranked Finals' winners
```{r fig.align='center', fig.height=5.5, fig.width=5.5}

selectInput('explore2',  '', c("Highest Ranked", "Lowest Ranked"))# Retrieve the variable to explore: victories or aces

renderPlotly({
  top_5_rank= Atp_ranks(atp, input$tournoi, input$explore2)  
  fig=top_5_vis(top_5_rank, "#1c8f7a", "total ascending", 'Rockwell', '#009966')    

  fig <- fig %>% layout(autosize = F,width = 400, height = 400)
  fig
    

})
```

### Victories according to the winner's hand
```{r}
renderPlotly({
  winner_hand_table <- victories_hand(atp, input$tournoi)
    
  colors = c("#00C5CD", "#458B74", "#7FFFD4")
  fig <-  plot_ly(winner_hand_table, marker = list(colors = colors))
  fig <- fig %>% add_pie(labels = ~winner_hand, values = ~count, hole = 0.5)
  fig
})
```
### Top 10 final appearances per country over the whole period
```{r}
  renderPlotly({
  Both=most_final_appearances(atp, input$tournoi)
  
  fig=final_appearance(Both, "Country", "Appearances", "group",  "grey10", c("#87CEFA","#00C5CD"),'Rockwell', '#009966')
  fig
})
```
### Greatest Rivalry
```{r}
DT::renderDataTable({
  most_freq_opposition=Restructure_Frequent_oppo(atp, input$tournoi )
  
  DT::datatable(most_freq_opposition,rownames = FALSE,fillContainer=FALSE, class = "cell-border compact", 
                options = list(pageLength = 3, dom = "t"))%>%
    formatStyle(1, target="row",backgroundColor =  styleEqual("Total rivalries","#008B8B")) %>%
    formatStyle(1, target="row",backgroundColor =  styleEqual("Player 2 wins", "#79CDCD"))%>%
    formatStyle(1, target="row",backgroundColor =  styleEqual("Player 1 wins" , "#97FFFF"))%>%
    formatStyle(columns=2, color="#104E8B", fontWeight="bold")
})
```


# ATP tour per year

# Players' view
